Hope

### 2024-06-03 paper/IEEES/paper.tex
more text

\usepackage{listings}
\usepackage{amsmath,amssymb,amsfonts}
\usepackage{algorithm}
\usepackage{algpseudocode}
\usepackage{graphicx}
\usepackage{textcomp}
\usepackage{xcolor}
\usepackage{listings}
\usepackage{url}
\usepackage{lstcoq}
\def\BibTeX{{\rm B\kern-.05em{\sc i\kern-.025em b}\kern-.08em
    T\kern-.1667em\lower.7ex\hbox{E}\kern-.125emX}}
\begin{document}
\title{Hope}

@@

%\textbf{Introduce here that sigma protocol is efficient and simple and all other details about sigma protocol.} 
Zero-knowledge proofs were first studied by Goldwasser, Micali, and Rackoff \cite{10.1145/22145.22178} and 
are possible for all problems in $NP$ \cite{10.1145/116825.116852}. Recall that $NP$ is the class of 
problems that have efficient verifiers; that is, for a given problem in the $NP$ class, there is 
a polynomial-time algorithm that can verify whether a given solution, or witness, to the problem is correct or not.
More formally, for a given $NP$-relation $R$ and a statement $x$, zero-knowledge proof allows a prover 
$P$ to convince a verifier $V$ that they posses a witness $w$ --polynomial in length of $x$-- such 
that ($x$, $w$) $\in$ $R$. To accomplish this, $P$ and $V$ engage in a 
interactive protocol and  at the end of the protocol $V$ either accepts or rejects the proofs.
\textit{Sigma protocol}, \textbf{shown in the figure }, is an efficient three move zero-knowledge proof where the 
verifier is assumed to be honest and characterised by completeness, (special) soundness, and 
(special honest-verifier) zero-knowledge. More formally: 
\begin{itemize}
  \item \textbf{Completeness:}
  when $P$ and $V$ follow the protocol, $V$ always accepts. 
  In other words, if $P$ knows $w$ for $x$ such that ($x$, $w$) $\in$ $R$,  
  then $P$ can successfully construct a proof $(a, c, r)$ that always passes the verification equation, 
  i.e., $V$ accepts.

@@

\textbf{Draw a picture here of sigma protocol}

@@

\section{The Coq Theorem Prover}
\textbf{FIXME:this seems too much of tutorial Coq so let me know your thoughts. We 
can explain MetaCoq here as well and the extraction to Rust and WebAssembly
so that it justifies this tutorial}
The Coq theorem prover \cite{the_coq_development_team} is a computer program that interacts with users, 
enabling them to encode mathematical definitions, express specifications (true statements) about 
these definitions, and formally prove that the definitions imply the specifications. 
A user first defines their mathematical object (definition) and then figure 
out some  true statements (specifications) about 
that object. Once the user has definition 
and specifications, they need to prove 
that the definition satisfies the specifications 
(proof writing). In general, amongst these three steps, 
the proof writing step is the most challenging and important step. 
During the proof writing, the user interacts with the Coq theorem prover 
via \emph{tactics}, a domain specific language 
to ease the proof writing. Even though the Coq theorem 
provides some amount of automation and proof 
search, most of the time it requires human assistance to finish the proof. 
It is one the most popular and robust theorem, and
one of reasons for its popularity is 
dependent types, that makes it possible to encode
any mathematical statement in its logic.
It has been used to verify many real world software projects and mathematical 
artefacts. For example, Coq has been used to 
formally verify CompCert \cite{10.1145/1111037.1111042}, 
a C compiler used by many companies\footnote{https://www.absint.com/partners.htm}, 
Fiat-Crypto \cite{8835346} 
used in BoringSSL --a cryptographic library used in Chrome, Android, 
and CloudFlare--, ConCert \cite{10.1145/3372885.3373829}, 
a smart contract certification framework, etc. \textbf{FIXME: More examples}

@@

So far we have just definitions of natural numbers and addition on them.
Now, it is time to define some specification (true statement) about
the addition operation, on natural numbers. From mathematical 
literature, we know that the addition operation on natural
numbers is associative and commutative. For simplicity, we
prove that our definition of addition on natural numbers is commutative, shown in 
Listing \ref{plus_comm}, and it is precisely the \emph{specification} for 
our addition operation.

@@

In Coq, \emph{Theorem} is the keyword
to define a specification, followed by the name (\emph{plus\_comm}). 
It says that for any two arbitrary natural numbers $m$ and $n$, 
encoded as \texttt{forall n m}, adding $n$ and $m$ is the same
as adding $m$ and $n$, encoded as \texttt{plus n m = plus m n}.
To write a formal proof of this statement, we tell the Coq theorem 
prover that we want to use the tactic language by 
stating the keyword \emph{Proof}. After finishing the proof, 
we use the keyword \emph{Qed} to inform Coq that our proof is 
finished. The moment Coq sees \emph{Qed},
it ensures that the proof is complete and correct according to its 
underlying logic. If we try to use Qed without finishing the proof,
Coq will not let us do so. Therefore, once we have Qed for any 
specification, by just trusting the Coq theorem prover we can be 
sure that our proof is correct. However, at this point, 
the curious reader can argue that why should we trust 
Coq because it is a computer program, similar any other 
computer program? Trusting Coq hinges on two things: 
(i) the meta theory, \emph{Calculus of Inductive Construction},
of Coq \cite{thierry1988calculus}
and (ii) its OCaml implementation \cite{the_coq_development_team}.
The meta theory of Coq has been scrutinised for decades
by many mathematicians and so far it has withstood all 
the scrutiny. The OCaml implementation of Coq  has a very 
small kernel and has been inspected by many computer scientists. 
In addition, there is a recent effort to develop more 
rigorous implementation for Coq proof checking \cite{10.1145/3371076} \textbf{FIXME: this is the place 
to state that we are following this path of MetaCoq}.

The keywords \emph{induction, intros, rewrite}
are tactics that are used to prove the statement that addition 
on natural numbers is commutative. 
The proof written between 
the keywords \emph{Proof} and \emph{Qed} amounts to the following: 
\begin{itemize}
  \item Base case: when $n$ is Zero, we need to prove that \texttt{plus Zero m = plus m Zero}
  \item Inductive case: when $n$ is Succ, we assume \texttt{plus m n = plus n m} 
      and we need to prove \texttt{plus (Succ m) n = plus n (Succ m)}
\end{itemize}  
\noindent
It is called proof by induction, and 
tactics are used to make the complicated 
process of proof writing easy.

\subsection{Schnorr Protocol Coq Encoding}

  We briefly explain the Schnorr protocol, which is very similar to figure \textbf{refer here to sigma protocol picture}.
  Given some public input $(G, g, q, h)$ where $G$
  is a cyclic group of prime order $q$, $g$ and $h$ are two 
  generators of the group $G$, the prover claims that they know a
  witness $w$ for the statement $h = g^w$; the existence of such
  a $w$ is immediate because $g$ generates the group. However,
  does the prover know the witness $w$? In order to convince the
  verifier, the prover and the verifier do the following:
  \begin{itemize}
    \item the prover picks a random number $u$, computes $a = g^u$,
    and sends $a$ to the verifier.
    \item the verifier picks a random challenge $c$ and sends it to
    the prover
    \item the prover computes $r = u + c * w$ and sends $r$ to the
    verifier
  \end{itemize}

@@

  \item special honest-verifier zero-knowledge proof:

@@

In the Schnorr protocol, $g, h, c$ are group elements from underlying group, while 
$u, e, t$ are scalar values from underlying prime field. In practice, 
both the group elements and the fields elements are some large prime numbers,
albeit the operations differ. For most of the languages it does not matter, 
but also a potential source of bugs (cite thomas work here). However, 
we need to flesh down all the details while encoding it Coq. One possibility is 
to encode the Coq functions to work with concrete numbers but this leads to 
cumbersome proofs because of dealing with concrete numbers. In our formalisation, 
we decided to abstract the underlying group as an abstract type $G$, endowed with 
usual group operation, and the underlying field as an abstract type $F$, endowed with 
filed operation. Finally, we abstract these two types in an vector space. This 
makes our formalisation generic that can be instantiated with 
any kind of group and field as long as it follows the axioms of 
vector space. For example, in our formalisation we have developed 
efficient algorithm for Schnorr group but our formalisation can 
later be also instantiated with elliptic curve group. However, 
one of the major benefit of this abstraction is easiness of proofs 
which can be easily automated. Therefore, we model the Schnorr 
protoco, the simulator, and the verification equation in Coq as follows:

@@

\noindent
 where $F$ is the underlying field, $G$ is the underlying group,
 $+ : F \rightarrow F \rightarrow F$ is field addition,
 $* : F \rightarrow F \rightarrow F$ is field multiplication, and
 $\mbox{\textasciicircum}: G \rightarrow F \rightarrow G$ scalar multiplication of vector space.  
 Recall that a vector space consists of a set of 
 vectors, denoted by \(V\), a field \(F\) (elements of F are called scalars), and 
 two operations: vector addition and scalar multiplication.
\begin{itemize}
    \item \textit{Vector addition}: for any vectors \(\mathbf{v}, \mathbf{w} \in V\), their sum, denoted by \(\mathbf{v} + \mathbf{w}\), is also in \(V\).
    \item \textit{Scalar multiplication}: for any vector \(\mathbf{v} \in V\) and any scalar \(c \in F\), their product, denoted by \(c\mathbf{v}\), is also in \(V\).
\end{itemize}

@@

We prove the completeness and special soundness property of the Schnorr protocol, 
as shown in Lisitng \cite{comp_sound}. We however cannot prove the special honest-verifier 
zero-knowledge property yet because it requires reasoning about probability that 
we discuss in the next section.

@@

  \subsection{Uniform Distribution}
  To reason about special honest-verifier zero-knowledge proof 
  intuitively, we need a model of uniform distribution. 
  we encode distribution a list of tuples where the 
  second element of tuple basically is probability of first element 
  in the tuple. Moreover, we define equality on distribution by 
  stating that two distributions are equal if they are permutation 
  of each other. Finally, we define a function , $uniform\_with\_replacement$, 
  to generate uniform distributions.

(* Probability Distribution on a type A *)
Definition dist (A : Type) : Type := list (A * prob).

(* Uniform distribution u*)
Definition uniform_with_replacement {A : Type} : 
  forall (l : list A), l <> [] -> dist A.
Proof.
  intros ? H.
  remember (Pos.of_nat (List.length l)) as len.
  exact (List.map 
    (fun x => (x, mk_prob 1 len)) l).
Defined.
\end{lstlisting}

We prove that the dist is a monad (\textbf{Cite some work}) by 
giving it a suitable definitions of ret and bind. Making 
it an instance of monad makes our life easier because 
we can compose a distribution $d$ $n$ times to 
returns a distribution on a vector of $n$ elements.

\begin{lstlisting}[frame=single, language=Coq, caption={Definition of Natural Number},
  label={ind_nat},captionpos=t, basicstyle=\ttfamily\footnotesize,
  abovecaptionskip=-\medskipamount]
(* Probability Monad *)
Definition Ret {A : Type} (x : A) : 
  dist A := [(x, one)].

@@

Now we have all the ingredients to prove the zero-knowledge 
proof of the Schnorr protocol. We define the 
Schnorr distribution $schnorr\_distribution$
that involves the secret $x$ and 
the simulator distribution $simulator\_distribution$
that does not involve the secret $x$. 
In the Schnorr distibution we draw 
a random field element $u$ from a uniform 
distribution $uniform\_with\_replacement \text{ }lf \text{ } Hlfn$
and use this $u$ to construct a distribution; 
similarly in the simulator distribution 
we draw a random field element $u$ from 
$uniform\_with\_replacement \text{ }lf \text{ } Hlfn$
and use it construct a distribution. Using these 
two definitions, we prove that these two 
distributions are identical 
$special\_honest\_verifier\_zkp$. However, 
contrary to informal reasoning, these two 
distributions are not syntactically equal but 
semantically equal. For both distributions, 
the first component is a transcript $(a, c, r)$ and 
the second component is a rational number that represents 
its probability. The triples in both distrubtions 
are an accepting transcript (semantic) but they 
are not identical and differ syntactically; 
therefore we first apply the 
$accepting\_conversation$ to the first pair of 
both distributions which turn them into 
a boolean value (true). After this  
application both distributions are identical 
that we prove.

@@

We shown in the function $repeat\_dist\_ntimes\_vector$.
  The reader can see from the proof 
  $uniform\_probability\_multidraw\_prob$
  that if a distribution $lf$ is repeated 
  $n$ times then the probability of this distribution 
  is $1/|lf|^n$. We use $repeat\_dist\_ntimes\_vector$ 
  when we combine multiple sigma protocols and 
  want to to prove zero-knowledge property. For example, 
  in Parallel composition when we combine $n$ sigma protocol 
  we need to need to draw a vector $n$ random numbers to 
  prove the zero-knowledge property.

@@

\subsection{Efficient Modular Arithmetic}
 As we stated that our formalisation is  
 abstract and can be instantiated with 
 a suitable group and field. In order 
 to run our code, we have developed 
 a formally verified Schnorr group (\textbf{cite here}). 
 \begin{lstlisting}[frame=single, language=Coq, caption={Definition of Natural Number},
  label={ind_nat},captionpos=t, basicstyle=\ttfamily\footnotesize,
  abovecaptionskip=-\medskipamount]
Section SchnorrGroup. 
  Context 
    {k p q : Z}
    {Hk : p = k * q + 1}
    {Hp : prime p}
    {Hq : prime q}.

  Record Schnorr_group := 
    mk_schnorr 
    {v : Z; Ha : 0 < v < p; 
    Hb : (v ^ q mod p = 1)}.

@@

  Definition mul_schnorr_group 
      (u v : Schnorr_group) : Schnorr_group.
  refine(
    match u, v with 
    | mk_schnorr au Hua Hub, 
      mk_schnorr av Hva Hvb => 
      mk_schnorr (Z.modulo (au * av) p) 
      (@multiplication_bound p Hp au 
      av Hua Hva)  _
    end).
  Defined.

@@

  (* Schnorr is a commutative Group *)
  Global Instance schnorr_comm : 
    @commutative_group 
    Schnorr_group (@eq Schnorr_group) 
    mul_schnorr_group one inv_schnorr_group.
  Proof. ... Qed.

Similarly, we have encoded a prime field.

@@

(* Prime Field *)
Section ZpField.

  Context 
    {p : Z}
    {Hp : prime p}.

  Definition zp_inv (x : Zp) : Zp.
    refine (match x with
      | mk_zp ax Hu => mk_zp 
        (Z.modulo 
          (Z.of_N (Npow_mod (Z.to_N ax) 
          (Z.to_N (p - 2)) (Z.to_N p)))
          p) _ 
    end).
    rewrite Zmod_mod.
    exact eq_refl.
  Defined.

  Definition zp_div (x y : Zp) : Zp :=
    zp_mul x (zp_inv y).

Finally, we prove that they form a vector space. 
We have encoded the scalar mulitplication of 
vector space as a pow function that takes an element from 
a Schnorr group and an element from 
a given field and returns an element in the 
Schnorr group.  The reader can see that our encoding eliminates all 
possibilities of mixing group and field, both represented 
as an integer modulo some large 
prime \cite{10.1007/978-3-662-63958-0_24}.

  Definition pow (g : @Schnorr.Schnorr_group p q) 
  (y : @Zpfield.Zp q) : @Schnorr.Schnorr_group p q.
  refine 
    match g, y with 
    | mk_schnorr gt Hgta Hgtb, Zpfield.mk_zp yt Hyt => 
      mk_schnorr  
      (Z.of_N (Npow_mod (Z.to_N gt) (Z.to_N yt) (Z.to_N p))) 
      (pow_subproof_first gt yt Hgta Hyt)
      (pow_subproof_second _ _  Hyt Hgta Hgtb)
    end.
  Defined.

@@

\section{Web Assembly and Rust from the Coq Formalisation (MetaCoq)}
  Bas Spitter

@@

\section{Related Work, Future Work, and Limitations}
  There are three work. Giles Barthe does not extract to executable code, 
  CryptoHol uses law of excluded middle, and thomas haines work is more about 
  verifying a transcript rather than constructing it. Moreover, 
  it does not reason about probabilities in intuitive way.

>>>>

\usepackage{listings}
\usepackage{amsmath,amssymb,amsfonts}
\usepackage{algorithm}
\usepackage{algpseudocode}
\usepackage{graphicx}
\usepackage{textcomp}
\usepackage{xcolor}
\usepackage{listings}
\usepackage{tikz}
\usetikzlibrary{positioning, arrows.meta}
\usepackage{url}
\usepackage{lstcoq}
\def\BibTeX{{\rm B\kern-.05em{\sc i\kern-.025em b}\kern-.08em
    T\kern-.1667em\lower.7ex\hbox{E}\kern-.125emX}}
\begin{document}
\title{Hope}

@@

%\textbf{Introduce here that sigma protocol is efficient and simple and all other details about sigma protocol.} 
Zero-knowledge proofs were first studied by Goldwasser, Micali, and Rackoff \cite{10.1145/22145.22178} and 
are possible for all problems in $NP$ \cite{10.1145/116825.116852}. Recall that $NP$ is the class of 
problems that have efficient verifiers; that is, for a given problem in the $NP$ class, there is 
a polynomial-time algorithm that can verify whether a given solution, or witness, to the problem is correct or not.
More formally, for a given $NP$-relation $R$ and a statement $x$, zero-knowledge proof allows a prover 
$P$ to convince a verifier $V$ that they posses a witness $w$ --polynomial in length of $x$-- such 
that ($x$, $w$) $\in$ $R$. To accomplish this, $P$ and $V$ engage in a 
interactive protocol and  at the end of the protocol $V$ either accepts or rejects the proofs.
\textit{Sigma protocol}, shown in the figure \ref{fig:sig_picture}, is an efficient three move zero-knowledge proof where the 
verifier is assumed to be honest and characterised by completeness, (special) soundness, and 
(special honest-verifier) zero-knowledge. More formally: 
\begin{itemize}
  \item \textbf{Completeness:}
  when $P$ and $V$ follow the protocol, $V$ always accepts. 
  In other words, if $P$ knows $w$ for $x$ such that ($x$, $w$) $\in$ $R$,  
  then $P$ can successfully construct a proof $(a, c, r)$ that always passes the verification equation, 
  i.e., $V$ accepts.

@@

\begin{figure}[ht]
  \centering
\begin{tikzpicture}
  \node (Prover)  {\textit{P (x, w)}} (0,0);
  \node (Verifier) [right=of Prover] at (4, 0) {\textit{V(x)}};
  % First arrow (left to right)
  \draw[->] (0,-0.5) -- (5,-0.5) node[midway, above] {\textit{commitment}};

  % Second arrow (right to left)
  \draw[->] (5,-1) -- (0,-1) node[midway, above] {\textit{challenge}};

  % Third arrow (left to right)
  \draw[->] (0,-1.5) -- (5,-1.5) node[midway, above] {\textit{response}};
\end{tikzpicture}
\caption{Sigma Protocol}
\label{fig:sig_picture}
\end{figure}

@@

\section{The Coq Theorem Prover}
\textbf{FIXME:this seems too much of tutorial Coq so let me know your thoughts. We 
can explain MetaCoq here as well and the extraction to Rust and WebAssembly
so that it justifies this tutorial}
The Coq theorem prover \cite{the_coq_development_team} is a computer program that interacts with users, 
enabling them to encode mathematical definitions, express specifications (true statements) about 
their definitions, and formally prove that the definitions imply the specifications. 
A user first defines their mathematical object (definition) and then figure 
out some  true statements (specifications) about 
that object. Once the user has definition 
and specifications, they need to prove 
that the definition satisfies the specifications 
(proof writing). In general, amongst these three steps, 
the proof writing step is the most challenging and important step. 
During the proof writing, an user interacts with the Coq theorem prover 
via \emph{tactics}, a domain specific language 
to ease the proof writing. Even though the Coq theorem 
provides some amount of automation and proof 
search, most of the time it requires human assistance to finish the proof. 
It is one the most popular and robust theorem, and
one of reasons for its popularity is 
dependent types, that makes it possible to encode
any mathematical statement in its logic.
It has been used to verify many real world software projects and mathematical 
artefacts. For example, Coq has been used to 
formally verify CompCert \cite{10.1145/1111037.1111042}, 
a C compiler used by many companies\footnote{https://www.absint.com/partners.htm}, 
Fiat-Crypto \cite{8835346} 
used in BoringSSL --a cryptographic library used in Chrome, Android, 
and CloudFlare--, ConCert \cite{10.1145/3372885.3373829}, 
a smart contract certification framework, etc. \textbf{FIXME: More examples}

@@

So far, we have defined natural numbers and addition. Now, we will specify 
some properties of addition on natural numbers. Mathematically, addition 
is known to be associative and commutative. For simplicity, we will 
prove that our addition definition is commutative, as shown in 
Listing \ref{plus_comm}, which serves as the specification for our 
addition operation.

@@

In Coq, \emph{Theorem} is the keyword used to define a specification, 
followed by the name (\emph{plus\_comm}). This specifies that for any 
two natural numbers $m$ and $n$ (encoded as \texttt{forall n m}), 
adding $n$ to $m$ is the same as adding $m$ to $n$ 
(encoded as \texttt{plus n m = plus m n}).
To write a formal proof of this statement, we start by indicating that 
we will use the tactic language with the keyword \emph{Proof}. Once the 
proof is complete, we use the keyword \emph{Qed} to signal to Coq that 
our proof is finished. At this point, Coq verifies that the proof is complete 
and correct according to its logic. If the proof is not finished, Coq will 
not accept \emph{Qed}. Therefore, having a \emph{Qed} for any specification 
ensures that our proof is correct, provided we trust the Coq theorem prover.
However, at this point, the curious reader can argue that why should we trust 
Coq because it is a computer program, similar any other computer program? 
Trust in Coq relies on two factors: (i) its meta-theory, the 
\emph{Calculus of Inductive Constructions} \cite{thierry1988calculus}, and 
(ii) its implementation in OCaml \cite{the_coq_development_team}.
The meta theory of Coq has been scrutinised for decades
by many mathematicians and so far it has withstood all 
the scrutiny, but not so much for its OCaml implementation \cite{coq_critical_bugs}. 
Therefore, there is a recent effort to develop more 
rigorous implementation for Coq proof checking \cite{10.1145/3371076} \textbf{FIXME: this is the place 
to state that we are following this path of MetaCoq and extraction}.

\subsection{Web Assembly and Rust from the Coq Formalisation (MetaCoq)}
  Bas

\subsection{Schnorr Protocol Coq Encoding}
  We briefly explain the Schnorr protocol, an interactive protocol 
  between a prover and a verifier, which follows the same structure as 
  depicted in Figure \ref{fig:sig_picture}. 
  Given some public input $G = (g, q, h)$ where $G$
  is a cyclic group of prime order $q$, $g$ and $h$ are two 
  generators of the group $G$, the prover claims that they know a
  witness $w$ for the statement $h = g^w$; the existence of such
  a $w$ is immediate because $g$ generates the group. However,
  does the prover know the witness $w$? In order to convince the
  verifier, the prover and the verifier do the following:
  \begin{itemize}
    \item the prover picks a random number $u$, computes $a = g^u$,
    and sends $a$ to the verifier.
    \item the verifier picks a random challenge $c$ and sends it to
    the prover
    \item the prover computes $r = u + c * w$ and sends $r$ to the
    verifier
  \end{itemize}

@@

  \item special honest-verifier zero-knowledge proof:
   the distribution for the conversations with an honest verifier --involving witness $w$--
   and the conversation with a simulator --without witness $w$-- are the same, given a 
   challenge $c$. We can 
   see this algebraically that both distributions \ref{f} and \ref{snd} have the identical 
   distribution, i.e., $1/q$. 
   \begin{align}\label{f}
    \{(a, c, r) \mid u \in_{R} Z_q ; a := g^u; r := u + c * w \}
   \end{align}
   \begin{align}\label{snd}
    \{(a, c, r) \mid u \in_{R} Z_q ; a := g^r * h^{-c}\}
   \end{align}

@@

In the Schnorr protocol, the elements $g$, $h$, and $a$ are group elements from the underlying group, while $u$, $c$, and $r$
are scalar values from the underlying prime field. In practice, both the group elements and the field elements are large 
numbers modulo some prime numbers, although the operations on them differ. 
One possibility is to encode the Coq functions to work with concrete numbers from the underlying group and field, 
but this leads to cumbersome proofs because of dealing with concrete numbers, but the bigger problem 
is that it is not modular. For most programming languages, this distinction 
may not be significant, but it can be a potential source of bugs \cite{10.1007/978-3-662-63958-0_24}. 
However, when encoding it in Coq, we need to thoroughly detail these distinctions because 
the same large number can belong to a group or field and that dictates what operations are available for them. 
Therefore, to avoid this unpleasant situation,  
we decided to abstract the underlying group as an abstract type $G$, endowed with 
usual group operation, and the underlying field as an abstract type $F$, endowed with 
filed operation in our formalisation. Moreover, we abstract these two types into a vector space for smooth interaction between 
group element and field element (exponential needs this). This 
makes our formalisation generic that can be instantiated with 
any kind of group and field as long as it follows the axioms of 
vector space. For example, in our formalisation we have developed 
efficient algorithm for the Schnorr group but our formalisation can 
later be also instantiated with elliptic curve group. However, 
one of the major benefit of this abstraction is easiness of proofs 
which can be easily automated. Therefore, we model the Schnorr 
protocol, the simulator, and the verification equation in Coq as follows:

@@

\noindent
 where $F$ is the underlying field, $G$ is the underlying group,
 $+ : F \rightarrow F \rightarrow F$ is the field addition,
 $* : F \rightarrow F \rightarrow F$ is the field multiplication, 
 $gop : G \rightarrow G \rightarrow G$ is the group operation, and
 $\mbox{\textasciicircum}: G \rightarrow F \rightarrow G$ is the scalar multiplication of vector space.  
 Recall that a vector space consists of a set of 
 vectors, denoted by \(V\), a field \(F\) (elements of F are called scalars), and 
 two operations: vector addition and scalar multiplication.
\begin{itemize}
    \item \textit{Vector addition}: for any vectors \(\mathbf{v}, \mathbf{w} \in V\), their sum, denoted by \(\mathbf{v} + \mathbf{w}\), is also in \(V\).
    \item \textit{Scalar multiplication}: for any vector \(\mathbf{v} \in V\) and any scalar \(c \in F\), their product, denoted by \(c\mathbf{v}\), is also in \(V\).
\end{itemize}

@@

We prove the completeness and special soundness property of the Schnorr protocol, 
as shown in Listing \cite{comp_sound}. However, to prove the special honest-verifier 
zero-knowledge property we need a model to reason about uniform probability 
distribution in Coq. We discuss the encoding of uniform probability distribution 
in the next section and subsequently explain the special honest-verifier zero-knowledge
proof.

@@

\subsection{Uniform Distribution}
To reason about special honest-verifier zero-knowledge proof 
intuitively, we need a model of uniform distribution. 
We follow the \cite{erwig2006functional}  and 
encode the distribution a list of tuples where the 
second element of tuple basically is probability of first element 
in the tuple. Moreover, we define equality on distribution by 
stating that two distributions are equal if they are permutation 
of each other. This encoding is flexible and allows us 
to encode any kind of distribution. We prove that the dist is a 
monad \cite{erwig2006functional} by 
giving it a suitable definitions of ret and bind. Making 
it an instance of monad makes our life easier because 
we can compose a distribution $d$ $n$ times to 
returns a distribution on a vector of $n$ elements. 
However, to reason about cryptographic primitives, we need uniform 
distribution and therefore we define a function, $uniform\_with\_replacement$, 
to generate uniform distributions, shown in Listing \ref{prob_def}.
We prove various prop

\begin{lstlisting}[frame=single, language=Coq, caption={Definition of Uniform Probability Distribution},
    label={prob_def},captionpos=t, basicstyle=\ttfamily\footnotesize,
    abovecaptionskip=-\medskipamount]
(* Probability Distribution on a type A *)
Definition dist (A : Type) : Type := 
 list (A * prob).

(* Probability Monad *)
Definition Ret {A : Type} (x : A) : 
  dist A := [(x, one)].

@@

(* Uniform distribution *)
Definition uniform_with_replacement {A : Type} : 
  forall (l : list A), l <> [] -> dist A.
Proof.
  intros ? H.
  remember (Pos.of_nat (List.length l)) as len.
  exact (List.map 
    (fun x => (x, mk_prob 1 len)) l).
Defined.
\end{lstlisting}

Now we have all the ingredients to prove special honest-verifier 
zero-knowledge proof of the Schnorr protocol. We define the 
Schnorr distribution $schnorr\_distribution$
that involves the secret $x$ and 
the simulator distribution $simulator\_distribution$
that does not involve the secret $x$. 
In the Schnorr distibution we draw 
a random field element $u$ from the uniform 
distribution $uniform\_with\_replacement \text{ }lf \text{ } Hlfn$,
where $lf$ is list of elements from which $u$
is drawn and $Hlf$ is a proposition that 
$lf$ is non-empty, and use it to construct 
a distribution on sigma protocol. Similarly, 
for the simulator distribution 
we draw a random field element $u$ from 
$uniform\_with\_replacement \text{ }lf \text{ } Hlfn$
and use it construct a distribution on sigma protocol. 
Using these two definitions, we prove that these two 
distributions are identical 
$special\_honest\_verifier\_zkp$. However, 
contrary to the reasoning in cryptographic papers, 
these two distributions are not syntactically equal but 
semantically equal. For both distributions, 
the first component is a transcript $(a, c, r)$ and 
the second component is a rational number that represents 
its probability. The triples in both distrubtions 
are an accepting transcript (semantic) but they 
are not identical and differ syntactically; 
therefore we first apply the 
$accepting\_conversation$ to the first pair of 
both distributions which turn them into 
a boolean value (true). After this  
application both distributions are identical 
that we prove.

@@

In the previous section, we explained the Schnorr proof, 
but we have also formalised a way to combine $n$ And, Or, Eq, 
and Parallel Schnorr statements. Proving special 
honest-verifier zero-knowledge proof is more challenging 
than a single Schnorr statement. One of the major challenge 
is to draw $n$ random element for an uniform distribution 
and therefore we have written the function $repeat\_dist\_ntimes\_vector$
that takes a distribution $dist\text{ }A$ and a number $n$ and a returns 
distribution of vectors of length $n$,  encoded as 
$dist \text{ } (Vector.t \text{ } A \text{ } n)$. The 
reader may notice that it is a generic function 
where distribution can be instantiated with 
any kind of distribution. However, in cryptography 
we are mostly concerned with uniform distribution and  
therefore in $uniform\_probability\_multidraw\_prob$ theorem
we instantiate the distribution with 
the uniform distribution $(uniform\_with\_replacement\text{ }lf\text{ }Hlf)$ and 
prove that the probability of this distribution 
is $1/|lf|^n$. We use it 
in Parallel composition where we combine $n$ sigma protocol and  
we need to need to draw a vector $n$ random numbers to 
prove the zero-knowledge property, as shown 
in $parallel\_schnorr\_distribution$.

@@

\subsection{Efficient Modular Arithmetic}
As stated earlier, to ensure the ease of proving, we worked with 
an abstract vector space. However, to execute this code, we need to 
instantiate the vector space with concrete examples. Therefore, we have 
encoded a prime field and the Schnorr group \cite{schnorr1991efficient} (mulitplicative 
group of integers modulo a large prime p) in the Coq theorem prover. 
To encode the Schnorr group, we postulate three integer $k, p, \text{ and } q$. 
Moreover, we assume $p \text{ and } q$ are primes where $p = k * q + 1$ (when 
$k = 2$, these primes are called Sophie Germain primes). Finally, 
we encode the neutral element $one$, the group multiplication $mul\_schnorr\_group$, 
and the group inverse $inv\_schnorr\_group$. We prove that our encoding 
of the Schnorr group in Coq is commutative group by making it 
an instance of the typeclass $schnorr\_comm$, 
which is an abstract typeclass that bundles the axioms 
of commutative group.

 \begin{lstlisting}[frame=single, language=Coq, caption={Coq Encoding of the Schnorr Group},
  label={ind_nat},captionpos=t, basicstyle=\ttfamily\footnotesize,
  abovecaptionskip=-\medskipamount]
Section SchnorrGroup. 
  Context 
    {k p q : Z} {Hk : p = k * q + 1}
    {Hp : prime p} {Hq : prime q}.

  Record Schnorr_group := mk_schnorr 
    {v : Z; Ha : 0 < v < p; 
    Hb : v ^ q mod p = 1}.

@@

  Definition mul_schnorr_group 
      (u v : Schnorr_group) : Schnorr_group.
  (* Proof terms omitted *)
  Defined.

@@

  (* Schnorr is a commutative Group *)
  Global Instance schnorr_comm : 
    @commutative_group 
    Schnorr_group (@eq Schnorr_group) 
    mul_schnorr_group one inv_schnorr_group.
  Proof. ... Qed. 
End SchnorrGroup.
\end{lstlisting}

In order to encode prime field, we postulate an integer $p$ and 
axiom that $p$ is prime. We encode the prime field as 
a record $Zp$ that contains an integer $v$ with an axiom 
that it is in the range of $[0 \ldots p)$. Moreover, 
we define all the operation of $Zp$ and prove that 
it is an instance of the typeclass $zp\_field$, which is 
a typeclass that encodes the axioms of a field.

\begin{lstlisting}[frame=single, language=Coq, caption={Coq Encoding of Prime Field},
  label={ind_nat},captionpos=t, basicstyle=\ttfamily\footnotesize,
  abovecaptionskip=-\medskipamount]
(* Prime Field *)
Section ZpField.
  Context 
    {p : Z} {Hp : prime p}.

  Global Instance zp_field : @field Zp zero 
    one zp_opp zp_add zp_sub zp_mul zp_inv zp_div.
End ZpField. 
\end{lstlisting}

Finally, we combine the Schnorr group and the prime field 
into a vector space instantiating the vector set with 
the Schnorr group and the scalar set with the prime field. 
However, in order to establish that it is an 
instance of vector space we need the definition 
of scalar mulitiplication. We encode the  
the scalar mulitplication $pow$ of 
vector space that takes an element from 
a Schnorr group and an element from 
the prime field and returns an element in the 
Schnorr group.  The reader can see that our encoding eliminates all 
possibilities of mixing group and field, both represented 
as an integer modulo some large 
prime \cite{10.1007/978-3-662-63958-0_24}.

@@

  Definition pow (g : @Schnorr.Schnorr_group p q) 
  (y : @Zpfield.Zp q) : @Schnorr.Schnorr_group p q.
  refine 
    match g, y with 
    | mk_schnorr gt Hgta Hgtb, mk_zp yt Hyt => 
      mk_schnorr  (Npow_mod gt yt p) 
      (pow_subproof_first _ _ Hgta Hyt)
      (pow_subproof_second _ _ Hyt Hgta Hgtb)
    end.
  Defined.

@@

@@

\section{Related Work, Future Work, and Limitations}
  Given the popularity of sigma protocol in voting 
  and other domains, it is not surprising that it has 
  been formalised in the past \cite{5552642,9519460,
  butler2021formalising,10.1145/3319535.3354247,287095,almeida2010certifying,10221929,
  10.1145/3594735}.

  Given the popularity of zero-knowledge in 
  privacy presearving computation such as voting, cryptocurrencies, 
  etc., it is not surprising that that sigma protocol and its other 
  variant (zk-SNARK) are an active area of research

  Given its popularity in voting, it is not surprising that 
  Sigma protocol is an active area of research \cite{5552642}.

  There are three work. Giles Barthe does not extract to executable code, 
  CryptoHol uses law of excluded middle, and thomas haines work is more about 
  verifying a transcript rather than constructing it. Moreover, 
  it does not reason about probabilities in intuitive way.
